%
% chapter introduction
%

This document is intended as a (more or less short) tutorial for the computer vision library \textbf{ICL} (\textbf{I}mage \textbf{C}omponent \textbf{L}ibrary). It will explain different aspects, that are useful to work with the ICL. The following outline shall give a short but documented overview over this document:

\begin{enumerate}
\item \textbf{What is the ICL:}\\ Here the underlying goals and ideas of the ICL will be presented.
\item \textbf{Feature Overview:}\\ The ICL provides a large set of features, packages, algorithms and utility classes. To motivate the reader for reading also the following chapters, the \emph{highlights} of the ICL are presented here.
\item \textbf{What is an Image:}\\ An image representation is fundamentally for the development of high performance computer vision algorihtms. It will be explained how the image representation is implemented in C++ as base class for ICL images. In particular it will be shown why we use template classes in combination with inheritance for the image class and, what problems arise therewith. 
\item \textbf{The Image class:}\\ Some functionalities are implemented as member functions, however most others are not. Here the ICL's image class interface is discussed.
\item \textbf{C++ Templates:}\\ To make later chapters more accessible, C++ template techniques are explained in detail. In particular, it will be shown, how templates are translated by the compiler, and how they can be used \small{\textbf{i)}} To reduce the amount of redundant source code and \small{\textbf{ii)}} To accelerate code without using constants for each possible parameter of functions.    
\item \textbf{Simple Image processing:}\\ How can simple Image processing algorithms be implemented (and how can they implemented elegantly) using the ICL.
\item \textbf{Overview over ICL Packages:}\\ The ICL consists of a set of (currently) 10 sub-packages that more or less base on each other. In this part, the contents and the basic ideas of these packages are introduced and explained. 
\item \textbf{Common ICL-classes and ICL-Interfaces:}\\ In many packages, interfaces (such as e.g. a \inlinecode{Grabber} for images -- a image source) are defined that influenced the design of the whole library heavily. These interfaces and also a variety of other very common classes and class sets are presented and explained.
\item \textbf{Graphical User Interfaces (GUI):}\\ The ICLQt package provides a powerful wrapper for Qt-based applications. In this part it will be shown, how simple and even more complex GUI's can be created and especially, how user input can be synchronized with the applications worker thread.
\item \textbf{Writing advanced applications:}\\ Here some advanced programming techniques are exemplified: Writing applications with GUI support, managing several threads, handling program arguments and much more.
\item \textbf{ICL-Development:}\\ICL developers need some deeper insights into the file structure and the makefile system. These information will be given in this part.
\item \textbf{ICL-Projects:}\\Development of ICL-bases applications can be performed very conveniently using a special makefile system and directory structure provided by the so called \emph{ICLProjects} svn branch. How to get these projects, how to add own projects here and how to include other projects and external libraries is shown in this (currently) last part. 
\end{enumerate} 

\section{What is the ICL}
Briefly said, the ICL is a C++ computer vision library. During design and development, two main design goals stood in the foreground [???]: \small{\textbf{i)}} Optimal Performance and \small{\textbf{ii)}} Simple and easy to use interfaces.
\subsection{Optimal Performance} 
Computer vision is one of the subjects, where even the processing power of modern multi-core CPU's can easily be exhausted. Therefore we decided to provide data interfaces that allow to implement algorithms as efficient as possible. In this context, three main aspects have to be mentioned:
\begin{enumerate}
\item \textbf{Providing the possibility of shallow data copies:}\\
When image data is obtained by other algorithms, modules or libraries, it must be possible to use this data (generally passed via pointers) directly without having to copy it deeply. Unfortunately there are two paradigms of storing and handling image data: \small{\textbf{i)}} Interleaved (here, several image channels are mixed and usually image data is allocated as a single data block; RGB image data is stored in RGBRGBRGB... manner) \small{\textbf{i)}} Planar (where each channel is stored in an own data block).\\
Of course, providing an image structure that is capable of working with both data formats natively would allow optimal performance. Unfortunately this would entail a large effort for implementing algorithms also supporting all these formats. Hence we decided to support only planar data layout supplemented with some very efficient conversion functions.
\item \textbf{Providing low-level data access:}\\
In contrast to the aspect above, we also provide low level data access to allow to pass ICL-image data to foreign algorithms shallowly (if these algorithms are able work with interleaved data. Otherwise we also provide fast conversion routines).
\item \textbf{Native but optional support for SIMD instruction sets:}\\
SIMD (Single Instruction Mutltiple Data)
\end{enumerate}

\subsection{Simple, easy to use object orientated interfaces:}


